---
title: "Boston Marathon"
output: html_document
---

```{r}
library(tidyverse)
library(viridis)
library(ggridges)
library(patchwork)
library(ggplot2)
library(scales)
library(dbplyr)
library(plotly)
```

```{r}
years_1 <- c(1900:2012, 2014)
years_2 <- c(2015:2019)

importing_data = function(x){
 
  if(str_detect(x, str_c(years_1, collapse = "|"))) {
  read_csv(x, na = c("NULL", "", "0"), col_types = "cicccciiiicc") 
  } 
  
  else if(str_detect(x, str_c(years_2, collapse = "|"))){
    read_csv(x, na = c("NULL", "", "0"), col_types = "cccicccccccccccccccccciiiiccc")
  }
}

boston_df <- 
  tibble(list.files("data", full.names = TRUE)) %>% 
  setNames("file_name") %>% 
  mutate(data = map(file_name, importing_data)) %>% 
  unnest(data) %>% 
  mutate(year = readr::parse_number(file_name),
         city = coalesce(city, residence),
         display_name = str_replace_all(display_name, "[^a-zA-Z0-9]", " ")) %>% 
  filter(!is.na(display_name)) %>% 
  select(-file_name, -residence, -first_name, -last_name)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Prepare age data

```{r}
boston_df_age_plot =
  boston_df %>% 
  select(age) %>%
  drop_na(age)
```

## Age distribution (counts)

This is plotly: 

```{r}
age_plotly_original = 
boston_df_age_plot %>% 
  count(age)  %>% 
 plot_ly(
      x = ~age, y = ~n, color = ~age,
      type = "bar", colors = "viridis") %>% 
  layout(
    xaxis = list(title = "Age"),
    yaxis = list(title = "Number of Participants")
)
```

This is plain ggplot:

```{r}
age_ggplot = 
ggplot(boston_df_age_plot, aes(x = age)) +
  geom_bar(fill = "cornflowerblue", 
                 color = "white") +
  labs(title = "Participants by age", 
       subtitle = "binwidth = 5 years",
       x = "Age", y = "Number of participants")

age_ggplot
```

This is plotly from ggplot: 

```{r}
ggplotly(age_ggplot)
```

This age plot will show the distribution of ages among participants. 

## Histogram of percentages by age 

```{r}
age_percentage_ggplot = 
  
ggplot(boston_df_age_plot, 
       aes(x = age, 
           y = ..count.. / sum(..count..))) +
  geom_histogram(fill = "cornflowerblue", 
                 color = "white", 
                 binwidth = 5) + 
  labs(title = "Participants by age", 
       y = "Percent",
       x = "Age") +
  scale_y_continuous(labels = percent)
```

```{r}
ggplotly(age_percentage_ggplot)
```

## Prepare gender plots

```{r}
boston_df_gender_plot =
    boston_df %>%
    select(gender) %>%
    mutate(gender = na_if(gender, "U"), 
            gender = recode(gender, m = "M"),
           gender = factor(gender, levels = c("M", "F"), labels = c("male", "female"))) %>% 
  drop_na(gender) %>% 
  count(gender)
```

## Participants by gender (%'s)

```{r}
bar_graph_gender = boston_df_gender_plot %>%
  mutate(pct = n / sum(n),
         pctlabel = paste0(round(pct*100), "%"))

# plot the bars as percentages, 
# in decending order with bar labels
ggplot(bar_graph_gender, 
       aes(x = reorder(gender, -pct),
           y = pct)) + 
  geom_bar(stat = "identity", 
           fill = "indianred3", 
           color = "black") +
  geom_text(aes(label = pctlabel), 
            vjust = -0.25) +
  scale_y_continuous(labels = percent) +
  labs(x = "Gender", 
       y = "Percent", 
       title  = "Participants by gender")
```

# Participants by gender (counts)

```{r}
ggplot(bar_graph_gender, 
       aes(x = gender, 
           y = n)) + 
  geom_bar(stat = "identity", 
           fill = "indianred3",
           color = "black") +
  geom_text(aes(label = n), 
            vjust = -0.5) +
 scale_y_continuous(labels = scales::comma) +
  labs(x = "Gender", 
       y = "Frequency", 
       title  = "Participants by gender")
```

## Prepare age change over time data

```{r}
boston_df_gender_year_plot =
    boston_df %>%
    select(year, gender) %>%
    mutate(gender = na_if(gender, "U"), 
            gender = recode(gender, m = "M"),
           gender = factor(gender, levels = c("M", "F"), labels = c("male", "female"))) %>% 
  drop_na(gender) %>%
  drop_na(year) %>%
  group_by(year, gender) %>%
  count()
```

## Gender change over time

```{r}
gender_age_plot =
ggplot(boston_df_gender_year_plot, aes(x = year, y = n)) + 
  geom_line(aes(color = gender), size = 1) + xlim(1960, 2019) + labs(x = "year", 
       y = "participants", 
       title  = "Gender over time")
```

```{r}
ggplotly(gender_age_plot)
```


## Prepare data for winning times

```{r}
winning_times_data =
    boston_df %>% 
    select(gender_result, gender, official_time, year) %>%
    mutate(gender = na_if(gender, "U"), 
            gender = recode(gender, m = "M"),
           gender = factor(gender, levels = c("M", "F"), labels = c("male", "female"))) %>% 
  drop_na() %>% 
  group_by(gender_result, gender, official_time, year) %>%
  mutate(as.numeric(official_time)) %>%
  filter(gender_result == 1) 
```


## Create plot

```{r}
winning_times_ggplot = 
  
ggplot(winning_times_data , aes(x = year, y = official_time, group = gender)) + 
  geom_line(aes(color = gender), size = 1) +  labs(x = "year", 
       y = "participants", 
       title  = "Winning times over time") +  theme(axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) 
```

```{r}
ggplotly(winning_times_ggplot)
```

