---
title: "Winner over time"
output: html_document
---

```{r}
library(tidyverse)
library(viridis)

library(plotly)
library(hms)
library(lubridate)

library(httr)
library(rvest)

knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE, 
  fig.width = 6, 
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "virids"
)

scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


```{r}
years_1 <- c(1900:2012, 2014)
years_2 <- c(2015:2019)

importing_data = function(x){
 
  if(str_detect(x, str_c(years_1, collapse = "|"))) {
  read_csv(x, na = c("NULL", "", "0"), col_types = "cicccciiiicc") 
  } 
  
  else if(str_detect(x, str_c(years_2, collapse = "|"))){
    read_csv(x, na = c("NULL", "", "0"), col_types = "cccicccccccccccccccccciiiiccc")
  }
}

boston_df <- 
  tibble(list.files("data", full.names = TRUE)) %>% 
  setNames("file_name") %>% 
  mutate(data = map(file_name, importing_data)) %>% 
  unnest(data) %>% 
  mutate(year = readr::parse_number(file_name),
         city = coalesce(city, residence),
         display_name = str_replace_all(display_name, "[^a-zA-Z0-9]", " ")) %>% 
  filter(!is.na(display_name)) %>% 
  select(-file_name, -residence)
```

### do you need hms or is it part of tidyverse?

```{r, warnings = FALSE}


winners_df = 
  boston_df %>% 
    mutate(
      year = as.factor(year),
      official_time = as_hms(official_time),
      pace = as_hms(pace),
      place_overall = as.numeric(place_overall)
      )

```

Make winners over time plot

* look at points 1990-2000 where time is ~1:20:00

```{r}
winners_df %>% 
  filter(overall == 1) %>% 
  arrange(year) %>% 
ggplot(aes(x = year, y = official_time, group = 1)) +
  geom_point() +
  geom_path() + 
 scale_x_discrete(breaks = c(1910, 1920, 1930, 1940, 1950, 1960, 1970, 1980, 1990, 2000, 2010, 2020))

winners_df %>%
  filter(overall == 1) %>% 
  arrange(official_time)
      
```

Jim Knaub and Franz Nietlispach reported as having an official time of 1:22:17 and 1:25:59 but 1:59 is the fastest marthon ever ran (though not recorded officially)

--> errors in data (~1:20:00 is fastes here but 1:59 is fasted -- but not recorded -- https://www.nytimes.com/2019/10/12/sports/eliud-kipchoge-marathon-record.html)

Plotly 



Fixing time variable -- plotly can't use lubridate 

```{r}
plotly_win_df = 
  boston_df %>% 
    mutate(
      official_time = as.POSIXct(official_time, format = "%H:%M:%OS"), 
      year = as.factor(year),
      pace = as.POSIXct(pace, format = "%H:%M:%OS"),
      place_overall = as.numeric(place_overall)
    )
  

```


making new plotly with reformatted time 

```{r, eval = TRUE}
boston_winners = 
plotly_win_df %>% 
  filter(overall == 1) %>% 
  plot_ly(x = ~year, y = ~format(official_time, "%H:%M:%OS"), 
          mode = 'lines', type = 'scatter',
          name = 'Boston Winners',
          hoverinfo = "text",
          text = 
            ~paste0("Name: ", display_name,
                    "\n", "Year: ", year,
            "\n", "Time: ", format(official_time, "%H:%M:%OS"),
            "\n", "Pace: ", format(pace, "%H:%M:%OS"))) %>% 
  layout(
    title = "Boston Marathon Winners by Year",
         xaxis = list(title = "Year"),
         yaxis = list(title = "Official Time"))

```




Marathon records -- adding new dataset 
```{r}


records_html = 
  read_html("https://www.topendsports.com/sport/athletics/record-marathon.htm")


record_marathon =
  records_html %>% 
  html_nodes("table") %>% 
  html_table(fill = T) %>% 
  lapply(., function(x) setNames(x, c("time", "date", "athlete", "country", "marathon"))) 

marathon = 
record_marathon %>% 
  as.data.frame() %>% 
  mutate(
    time = as_hms(time),
  ) %>% 
  separate(date, into = c("month", "day", "year")) %>% 
    mutate(year = as.numeric(year)) %>% 
    select(-month, -day)

marathon %>% 
plot_ly(type = 'scatter', mode = 'lines', text = ~paste('Name: ', athlete)) %>% 
  add_trace(x = ~year, y = ~time)%>% 
  layout(yaxis = list(categoryorder = "array", categoryarray = winners_df$official_time))


library(purrr)
library(lubridate)


  

```



age x year (intervals?)
pace x year plot?
Boston winner compared to record winner overall - 